Classification of short product Reviews using Semi-Supervised Learning

### 2012-09-03 docs/paper.tex
Abstract added, format modified

\author{David Przybilla\\dav.alejandro@gmail.com, davida@coli.uni-saarland.de\\ \\ Term Paper for Unsupervised Semi-supervised
Learning Seminar\\ Universit\"{a}t des Saarlandes}
\title{Classification of short product Reviews using Semi-Supervised Learning}
\begin{document}
\twocolumn[
	 \begin{@twocolumnfalse}
    \maketitle
   \begin{abstract}
      ...
    \end{abstract}
  \end{@twocolumnfalse}
 ]

@@

In ~\cite{Ando:2005:FLP:1046920.1194905} Zhang and Kubota proposed a semi-supervised approach using linear classifiers for multiple learning tasks.\\

@@

Though Classifying text has been a widely studied topic,the focus has been on long documents,

@@

\section{Structure Learning}
A Semi-supervised learning method proposed in ~\cite{Ando:2005:FLP:1046920.1194905}.\\
This paper proposes a way to learn multiple classification tasks.In this approach the original Classification Task(Target Problem) is extended by creating a set of auxiliary classification tasks.\\
The Auxiliary Classification tasks are used to improve performance on the target task,
the underlying assumption is that by solving the auxiliary problems one should be able to find good predictive structures.\\
The Auxiliary Tasks are trained on the unlabelled data,in consequence one constraint to the creation of auxiliary tasks is that they should be able to automatically generate training data from the target's problem unlabelled data.In ~\cite{Ando:2005:HSL:1219840.1219841} it is argued that having a high number of auxiliary tasks is beneficial for the performance.\\
\\
In this paper's experiment, the target task corresponds to find the label of each comment.\\
The auxiliary problems are defined as:\\
Learn a linear predictor using the Unlabelled data for the $K$ most common words in the unlabelled data and a predictor for the words with highest Pointwise mutual information(PMI) from the Labelled Data.\\
By doing this both the features of the labelled data and unlabelled data will be extended, the labelled data will be extended with features from the unlabelled data, and the unlabelled data will be extended with predictive features of the labelled data.\\
\\
For learning this tasks, first the Words with highest PMI are found using the labelled data, then the words with highest frequency in the unlabelled data are found.\\
Subsequently a linear classifier for predicting each of this words is trained using the unlabelled data.
It is clear that labels for this tasks can be easily generated by masking the words for which the classifiers are being trained to predict.\\
\\
By solving the auxiliary tasks, the feature vectors of the training data for the target problem can be extended with the predictions of the auxiliary tasks.\\
This might shown useful in the setup of the experiment, since we are extending the feature representations from knowledge of unlabelled data.\\
\\
Finally a linear classifier is learnt using the training data for the target problem.\\
With respect to the ASO-SVD algorithm, this paper just explore a naive approach by using auxiliary problems, in this regard the auxiliary classifiers are used to extend the feature vectors.\\
For the rest of the paper we will refer to this approach as Naive SL.

>>>>

\author{David Przybilla\\dav.alejandro@gmail.com, davida@coli.uni-saarland.de\\ \\ Term Paper for Unsupervised Semi-supervised
Learning Seminar\\ Universit\"{a}t des Saarlandes}
\title{Classification of short product Reviews using Semi-Supervised Learning}
\begin{document}
\twocolumn[
	 \begin{@twocolumnfalse}
    \maketitle
  \end{@twocolumnfalse}
 ]

   \begin{abstract}
      Microblogging has become a trend,thus many users are using such platforms to share their opinions.Mining these opinions can reveal valuable information to companies, such as what features to develop in their products or marketing strategies.However there are  major drawbacks when mining tweets, first their length do not provide enough word occurrences so traditional bag-of-words methods have limitations, second they are extremely noisy,and third annotated data is limited and costly to get.\\
      In this paper we address the problem of classifying short product reviews by using semisupervised learning. A Comparison among two semisupervised methods and a supervised method is given. Finally we propose different ways to improve the given results by injecting knowledge into the semisupervised models.
    \end{abstract}

@@

Zhang and Kubota ~\cite{Ando:2005:FLP:1046920.1194905} proposed a semi-supervised approach using linear classifiers for multiple learning tasks.\\

@@

Even though Classifying text has been a widely studied topic,the focus has been on long documents,

@@

\section{Structure Learning}
A Semi-supervised learning method proposed in ~\cite{Ando:2005:FLP:1046920.1194905}.\\
This paper proposes a way to learn multiple classification tasks.In this approach the original Classification Task(Target Problem) is extended by creating a set of auxiliary classification tasks.\\
The Auxiliary Classification tasks are used to improve performance on the target task,
the underlying assumption is that by solving the auxiliary problems one should be able to find good predictive structures.\\
The Auxiliary Tasks are trained on the unlabelled data,in consequence one constraint to the creation of auxiliary tasks is that they should be able to automatically generate training data from the target's problem unlabelled data.In ~\cite{Ando:2005:HSL:1219840.1219841} it is argued that having a high number of auxiliary tasks is beneficial for the performance.\\
\\
In this paper's experiment, the target task corresponds to find the label of each comment.\\
The auxiliary problems are defined as:\\
Learning a linear predictor using the Unlabelled data for the $K$ most common words in the unlabelled data and a predictor for the words with highest Pointwise mutual information(PMI) from the Labelled Data.\\
By doing this both the features of the labelled data and unlabelled data will be extended, the labelled data will be extended with features from the unlabelled data, and the unlabelled data will be extended with predictive features of the labelled data.\\
\\
For learning this tasks, first the Words with highest PMI are found using the labelled data, then the words with highest frequency in the unlabelled data are found.\\
Subsequently a linear classifier for predicting each of this words is trained using the unlabelled data.
It is clear that labels for this tasks can be easily generated by masking the words for which the classifiers are being trained to predict.\\
\\
By solving the auxiliary tasks, the feature vectors of the training data for the target problem can be extended with the predictions of the auxiliary tasks.\\
This might shown useful in the setup of the experiment, since we are extending the feature representations from knowledge of unlabelled data.\\
\\
Finally a linear classifier is learnt using the training data for the target problem.\\
With respect to the ASO-SVD algorithm, this paper just explore a naive approach by using auxiliary problems, in this regard the auxiliary classifiers are used to extend the feature vectors.\\
For the rest of the paper we will refer to this approach as Naive SL.
